Bone-Conduction Audio Interface to\\Guide People with Visual Impairments

### 2019-07-15 paper.tex
Fixed legacy sentance

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous experimental results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.25}{\radian} and \SI{0.36}{\radian} for groups \textit{G1} and \textit{G2}, respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 63\% and 47\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a more modest improvement of 43\% in \textit{G1} and 16\% for \textit{G2} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization}.
However, all the participants in~\cite{stanley2006lateralization} had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for group \textit{G2} are centred around the negative angle, as shown in \cref{fig:err-results}, indicating a possible underlying bias either in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization}. Further investigation with a larger participant pool is needed to determine this underlying bias, if any.

>>>>

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous experimental results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.25}{\radian} and \SI{0.36}{\radian} for groups \textit{G1} and \textit{G2}, respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 63\% and 47\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a more modest improvement of 43\% in \textit{G1} and 16\% for \textit{G2} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization}.
However, all the participants in~\cite{stanley2006lateralization} had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for both groups are centred around the negative angle, as shown in \cref{fig:err-results}, indicating a possible underlying bias either in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization}. Further investigation with a larger participant pool is needed to determine this underlying bias, if any.
